\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=1.45cm]{geometry}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\setmainfont{TeX Gyre Termes}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedright
\raggedbottom
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\linespread{1.04}

\definecolor{ink}{HTML}{111827}
\definecolor{muted}{HTML}{4B5563}

\hypersetup{
	colorlinks=true,
	urlcolor=ink,
	linkcolor=ink,
	pdfauthor={Marco S\`evegrand},
	pdftitle={Marco S\`evegrand - Curriculum Vitae}
}

\titleformat{\section}{\vspace{0.45em}\large\bfseries\color{ink}}{}{0pt}{}[\color{ink}\titlerule\vspace{0.2em}]
\titlespacing*{\section}{0pt}{0.55em}{0.2em}

\newcommand{\resumeItem}[1]{
	\item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
	\item
		\begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
			\textbf{#1} & {\small #2} \\
			\textit{\small #3} & \textit{\small #4} \\
		\end{tabular*}\vspace{-0.45em}
}

\newcommand{\resumeProjectHeading}[2]{
	\item
		\begin{tabularx}{\textwidth}[t]{@{}Xr@{}}
			\small #1 & {\small #2} \\
		\end{tabularx}\vspace{-0.2em}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}, itemsep=0.55em, topsep=0.25em, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.15em, itemsep=0.16em, topsep=0.28em, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0.2em}}
\newcommand{\iconlink}[3]{\href{#1}{#2\hspace{0.35em}#3}}
\newcommand{\resumeMetaLine}[1]{\vspace{-0.15em}{\small\color{muted}[#1]}\par\vspace{0.05em}}
\newcommand{\resumeTechLine}[1]{\vspace{0.2em}{\small\color{muted}#1}\par\vspace{0.01em}}

\begin{document}

\begin{center}
	{\Huge \scshape Marco S\`evegrand} \\
	\vspace{3pt}
	{\small\color{muted} Software Engineer $|$ Infrastructure \& Systems $|$ Cybersecurity} \\
	\vspace{5pt}
	\small Braga, Portugal $|$ (+351) 928 116 840 $|$ \href{mailto:marcosevegrand@pm.me}{marcosevegrand@pm.me} \\
	\vspace{1pt}
	\small \iconlink{https://marcosev.com}{\faGlobe}{marcosev.com} $|$ \iconlink{https://linkedin.com/in/marcosevegrand}{\faLinkedin}{marcosevegrand} $|$ \iconlink{https://github.com/marcosevegrand}{\faGithub}{marcosevegrand}
\end{center}

\section{About Me}
\small Software engineering graduate focused on infrastructure, networking, application security, and secure software development lifecycles. Gaining experience with Linux VPS environments, CI/CD pipelines and full-stack development. Currently pursuing Azure certification and enrolling in a Master's in Cybersecurity.

\section{Experience}
\resumeSubHeadingListStart
	\resumeSubheading
		{Full-Stack Web Developer (Part-time)}{Feb 2026 -- Present}
		{Biobrassica}{Braga, Portugal}
		\resumeItemListStart
			\resumeItem{Sole developer for the company's online presence: built a full branding page and e-commerce store with product CRUD, inventory management, and secure payment integration via IfThenPay.}
			\resumeItem{Initially developed with Django/Python on a Linux VPS; currently migrating the stack to Laravel/PHP on cPanel to simplify maintenance and handover.}
		\resumeItemListEnd

	\resumeSubheading
		{Store Associate (Part-time)}{Feb 2026 -- Present}
		{Biobrassica}{Braga, Portugal}
		\resumeItemListStart
			\resumeItem{Oversaw stock management and replenishment, ensuring consistent product availability.}
			\resumeItem{Delivered front-line customer service, handling inquiries and in-store sales.}
		\resumeItemListEnd

	\resumeSubheading
		{Math \& Physics Tutor (Self-employed)}{Sep 2025 -- Present}
		{}{Remote}
		\resumeItemListStart
			\resumeItem{Mentored high-school students in mathematics and physics through one-to-one lessons.}
			\resumeItem{Designed study plans aligned to each student's exam goals and skill level.}
		\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education \& Credentials}
\resumeSubHeadingListStart
	\resumeSubheading
		{B.Sc. Software Engineering}{Sep 2023 -- Jun 2026}
		{University of Minho}{Braga, Portugal}
		\resumeItemListStart
			\resumeItem{Final grade: 16/20. Coursework includes distributed systems, cybersecurity, operating systems, compilers, algorithms, databases, AI, and software systems design.}
		\resumeItemListEnd

	\resumeSubheading
		{Secondary Education}{Sep 2020 -- Jun 2023}
		{Escola Secundária Fernão de Magalhães}{Braga, Portugal}
		\resumeItemListStart
			\resumeItem{Final grade: 19.6/20. Participated in Mathematics Olympiads, Chemistry Olympiads, and Youth Parliament.}
		\resumeItemListEnd

	\resumeSubheading
		{English C1 Advanced}{May 2023}
		{Cambridge Assessment English}{Certification ID: C1827928}
		{}

	\resumeSubheading
		{Author -- \href{https://marcosevegrand.linkyhost.com}{``Mistério no Aeroclube''}}{2019}
		{Published fiction book (80 pages, teen demographic)}{}
		{}
\resumeSubHeadingListEnd

\section{Skills}
\small
\textbf{Core Languages} \hspace{0.4em} Go \& C. \\[0.15em]
\textbf{Systems \& Infrastructure} \hspace{0.4em} Linux, Docker, VPS. \\[0.15em]
\textbf{Architecture \& Security Concepts} \hspace{0.4em} Concurrent Programming, Network Protocols, Applied Cryptography, Threat Modeling. \\[0.15em]
\textbf{Currently Learning} \hspace{0.4em} Kubernetes, Azure Cloud Services. \\[0.15em]
\textbf{Soft Skills} \hspace{0.4em} Proactive, clear communication, active listening, critical thinking, learning agility \\[0.15em]
\textbf{Spoken Languages} \hspace{0.4em} Portuguese (Native), English (C1)

\section{Selected Projects}
\resumeSubHeadingListStart
	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/SSI2526}{\faGithub}\hspace{0.3em}\textbf{Secure Multi-Device Messaging Platform}}{[Grade: 18/20, B+]}
		\resumeTechLine{Python, TCP/TLS, E2EE, X3DH, Ed25519, X25519, AES-GCM, Argon2id, SQLite, Textual}
		\resumeItemListStart
			\resumeItem{Built an end-to-end encrypted messaging system with multi-device identity, offline delivery, group messaging, local history, and a terminal TUI.}
			\resumeItem{Implemented X3DH session bootstrap, symmetric ratcheting, device challenge-response authentication, certificate-based identity binding, and at-rest encryption for client/server secrets.}
		\resumeItemListEnd

	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/ATS2526}{\faGithub}\hspace{0.3em}\textbf{Automated Software Testing \& Quality Analysis Pipeline}}{[Grade: 18.5/20, A-]}
		\resumeTechLine{Java, Maven, JUnit 5, jqwik, JaCoCo, PIT, EvoSuite, Make}
		\resumeItemListStart
			\resumeItem{Strengthened two Java applications with unit tests, property-based tests, coverage analysis, mutation testing, and automated test generation.}
			\resumeItem{Automated the full quality pipeline with Maven/Make, expanding the suite to 444 tests and achieving PIT mutation scores of 76\% and 85\% across the two projects.}
		\resumeItemListEnd

	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/SO2425}{\faGithub}\hspace{0.3em}\textbf{Document Indexing and Search Service}}{[Grade: 20/20, A+]}
		\resumeTechLine{C, Linux, POSIX IPC, FIFOs, LRU Cache, Concurrency}
		\resumeItemListStart
			\resumeItem{Built a Linux document indexing service around FIFO-based client-server communication with persistent indexing for stateful retrieval.}
			\resumeItem{Added an LRU cache and parallel keyword search, with process cleanup and concurrency control for safe multi-document execution.}
		\resumeItemListEnd

	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/CC2526}{\faGithub}\hspace{0.3em}\textbf{Space Communication Protocols \& Simulator}}{[Grade: 19.5/20, A+]}
		\resumeTechLine{Go, TCP/UDP, React, Node.js, CORE Emulator, FEC}
		\resumeItemListStart
			\resumeItem{Designed custom TCP and UDP protocols with FEC, fragmentation, ordered delivery, and exponential backoff retransmission.}
			\resumeItem{Simulated a mothership-rover mission architecture and built a real-time dashboard validated in CORE under packet loss and latency.}
		\resumeItemListEnd

	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/LI42526}{\faGithub}\hspace{0.3em}\textbf{LLM-Assisted Software Development Lifecycle}}{[Grade: 19/20, A]}
		\resumeTechLine{TypeScript, React, Fastify, PostgreSQL, Prisma, Zod, Turborepo, LLM-Augmented Engineering}
		\resumeItemListStart
			\resumeItem{Conducted a complete software development lifecycle from requirements through architecture, implementation, testing, and documentation, using structured LLM assistance from Claude, GitHub Copilot, and Stitch AI; catalogued and critically reviewed all 48 prompts.}
			\resumeItem{Applied a three-pillar methodology of upfront planning, strict modular decomposition, and mandatory human review on every LLM output, explicitly distinguishing the approach from unstructured ``vibe coding.''}
			\resumeItem{Selected among the top 4 projects in the curricular unit and featured at the ES3A workshop, held as part of Universidade do Minho's Departamento de Inform\'atica 50th-anniversary celebrations.}
		\resumeItemListEnd

	\resumeProjectHeading
		{\href{https://github.com/marcosevegrand/SD2526}{\faGithub}\hspace{0.3em}\textbf{Distributed Time-Series Storage System}}{[Grade: 18/20, B+]}
		\resumeTechLine{Java, TCP, Multithreading, Thread Pool, Pub/Sub, Persistence}
		\resumeItemListStart
			\resumeItem{Built a concurrent multi-client TCP server with a custom framed protocol, thread-pool execution, and safe shared-state handling.}
			\resumeItem{Developed a configurable time-series storage engine with in-memory caching, disk persistence, and real-time pub/sub notifications.}
		\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
